\begin{abstract}

  The \bundle{} and \bundlep{} scheduling algorithms are cache-cognizant
  thread-level scheduling algorithms and associated worst case
  execution time and cache overhead (WCETO) techniques for hard
  real-time multi-threaded tasks. The \texttt{BUNDLE}-based approaches
  utilize the inter-thread cache benefit to reduce WCETO values for 
  jobs. Currently, the \texttt{BUNDLE}-based approaches are limited to
  scheduling a single task. This work aims to expand the applicability
  of \texttt{BUNDLE}-based scheduling to multiple task multi-threaded
  task sets.

  \texttt{BUNDLE}-based scheduling leverages knowledge of potential
  cache conflicts to selectively preempt one thread in favor of
  another from the same job. This thread-level preemption is a
  requirement for the run-time behavior and WCETO calculation to
  receive the benefit of \texttt{BUNDLE}-based approaches. This work
  proposes scheduling \texttt{BUNDLE}-based jobs non-preemptively
  according to the earliest deadline first (EDF) policy. Jobs are
  forbidden from preempting one another, while threads within a job
  are allowed to preempt other threads.

  An accompanying schedulability test is provided, named Threads Per
  Job (\tpj{}). \tpj{} is a novel schedulability test, input is a task
  set specification which may be transformed (under certain
  restrictions); dividing threads among tasks in an effort to find
  a feasible task set. Enhanced by the flexibility to transform task
  sets and taking advantage of the inter-thread cache benefit, the
  evaluation shows \tpj{} scheduling task sets fully preemptive EDF
  cannot. 
  
\end{abstract}
